---
title: "Workout3"
author: "Zhe Chen"
output: github_document
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```


## Overview

"binomal" is a minimal R package that provides functions to calculate probabilities of a Binomial random variable, and related calculations such as the probability distribution, the expected value, variance.

## Installation

Install the development version from GitHub via the package "devtools":

```{r}
# development version from GitHub:
#install.packages("devtools") 
# install "cointoss" (without vignettes)
devtools::install_github("stat133-sp19/hw-stat133-Zhe-Chen-karen/binomial")
# install "cointoss" (with vignettes)
devtools::install_github("stat133-sp19/hw-stat133-Zhe-Chen-karen/binomial", build_vignettes = TRUE)
```

## Main functions

* bin_mean(): compute the mean of a binomail distribution
* bin_variance(): compute the varince of a binomail distribution
* bin_mode(): compute the mode of a binomail distribution
* bin_skewness(): compute the skewness of a binomail distribution
* bin_kurtosis(): compute the kurtosis of a binomail distribution
* bin_choose(): compute the number of combinations in which k successes can occur in n trials
* bin_probability(): compute the probability of getting k successes in n trials with specific probability of success.
* bin_distribution(): returns a data frame with the probability distribution
* bin_cumnulative(): returns a data frame with both the probability distribution and the cumulative probabilities
* bin_variable(): returns an object of class "binvar", that is, a binomial random variable object
* plot.bincum(): graphs the cumulative distribution of an object "bincum"
* plot.bindis(): graphs a barplot to display the probability histogram of a binomial distribution object bindis
* summary.binvar(): shows a full summary description of the object binvar

## Usage

```{r}
library(binomial)
#functions of measure
bin_mean(10, 0.3)
bin_variance(10, 0.3)
bin_mode(10, 0.3)
bin_skewness(10, 0.3)
bin_kurtosis(10, 0.3)

#compute the number of combinations in which k successes can occur in n trials
bin_choose(n = 5, k = 3)

#compute the probability of getting k successes in n trials with specific probability of success
bin_probability(success = 3, trials = 10, prob = 0.3)

#show probability distribution
bin_distribution(trials = 5, prob = 0.5)
dis1 <- bin_distribution(trials = 5, prob = 0.5)
plot(dis1)

#show the cumulative probabilities
bin_cumulative(trials = 5, prob = 0.5)
dis2 <- bin_cumulative(trials = 5, prob = 0.5)
plot(dis2)

#generate a binomial random variable object
bin1 <- bin_variable(trials = 10, p = 0.3)
bin1

#summary
summary(bin1)
```
