---
title: "Getting Started With Binomial Package"
author: "Zhe Chen"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to binomial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo=FALSE, message=FALSE}
knitr::opts_chunk$set(collapse = T,comment = "#>")
library(binomial)
```

## Binomial

The package "binomial" is an implementation for computing the probability of a binomial random variable, summarizing its related statistics and visualizing the probability distribution and cumulative probability distribution.

## Functions of measure

You can use the following functions to get the mean, variance, mode, skewness and kurtosis of a binomial distribution with specified trials and probability.

```{r}
#mean
bin_mean(10, 0.3)
#variance
bin_variance(10, 0.3)
#mode
bin_mode(10, 0.3)
#skewness
bin_skewness(10, 0.3)
#kurtosis
bin_kurtosis(10, 0.3)
```

## Function bin_choose()

You can use function bin_choose() to compute the number of combinations in which k successes can occur in n trials.

```{r}
bin_choose(n = 5, k = 2)
```

## Function bin_probability()

You can use function bin_probability() to compute the probability of getting k successes in n trials with specific probability of success.

```{r}
bin_probability(success=3,trials=5,prob=0.5)
```

## Creating a binomial random variable object

The function bin_variable() gives you an object of class "binvar", that is, a binomial random variable object.

```{r}
bin1<-bin_variable(trials=5,prob=0.5)
bin1
```

## Show the summary of binomial variable

Function `summary()` gives you a summary of parameters and measures of a binomial variable object.

```{r}
summary(bin1)
```

## Show the table of binomial distribution

You can use the function bin_distribution() to show a table of binomial distribution, where the first column is sucesses and the second column is probability.

```{r}
dist1=bin_distribution(trials=5,prob=0.5)
dist1
```

##Show the table of cumulative distribution

You can use the function bin_cumulative() to return a data frame with both the probability distribution and the cumulative probabilities (sucesses in the first column, probability in the second column, and cumulative in the third column).

```{r}
dist2=bin_cumulative(trials=5,prob=0.5)
dist2
```

## Plotting binomial distribution

Method plot.bindis() shows the barplot to display the probability histogram of a binomial distribution object "bindis".

```{r}
# plotting binomial probability distribution
dist1=bin_distribution(trials=5,prob=0.5)
plot(dist1)
```

Method plot.bincum() shows the plot of cumulative distribution in an object "bincum".

```{r}
# plotting binomial cumulative distribution
dist2 <- bin_cumulative(trials = 5, prob = 0.5)
plot(dist2)
```
